Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-12-07 paperDraft3.tex
removed failure types from intro

The JLTV has been through a series of test events as it has been developed.
Engineering and Manufacturing Development (EMD) included three phases of
testing, where fixes occurred only during a set Corrective Action Period (CAP)
between each phase. For every vehicle, each failure encountered during testing
was recorded and attributed to a specific failure mode. Failures discovered
during mission execution that result in an abort or termination of a mission in
progress are scored as Operational Mission Failures (OMF), and failures of
mission essential components are scored as Essential Function Failures (EFF).
The EFFs tend to include a large portion of the failure modes that drive
maintenance costs and reduce system availability. While requirements are
typically written in terms of OMFs, because OMFs are by definition EFFs that
occurred at critical times, combining the failures provides a more robust
reliability estimate. Since fixes were delayed to CAPs, analysis generally shows
a distinct jump in the system reliability between test phases.

@@

There are 91 OMFs and 1321 EFFs attributed to 26 failure modes recorded across
all eight vehicles and all three test phases. In any given phase of test, every
vehicle is not guaranteed to have a failure of all 26 failure modes, and each
test phase does not necessarily end with a failure. Therefore, we have 624 right
censored observations, accounting for miles driven without observed failures.

>>>>

The JLTV has been through a series of test events as it has been developed.
Engineering and Manufacturing Development (EMD) included three phases of
testing, where fixes occurred only during a set Corrective Action Period (CAP)
between each phase. For every vehicle, each failure encountered during testing
was recorded and attributed to a specific failure mode.  Since fixes were
delayed to CAPs, analysis generally shows a distinct jump in the system
reliability between test phases.

@@

There are 1412 observed failures attributed to 26 failure modes recorded across
all eight vehicles and all three test phases. In any given phase of test, every
vehicle is not guaranteed to have a failure of all 26 failure modes, and each
test phase does not necessarily end with a failure. Therefore, we have 624 right
censored observations, accounting for miles driven without observed failures.
